### 2019-11-07 paper-body.tex
Updated: Further expanded section on considered solutions

\subsection{Both servers simulate objects in an overlapping region}
Simulate objects overlapping the boundary and objects interacting with those on both servers, e.g. by using an overlapping region. Object may interact with objects not in the overlapping region, so the results would diverge or the overlapping region would have to dynamically change in order to keep all interacting objects within the overlapping region. Even if all objects interacting were in the overlapping region, results would still diverge due to non-determinism of physics engines. The divergence of results due to non-determinism could be corrected by periodically syncing the objects (ensuring the objects have the same state on both servers), however, this would appear as jitter and would require additional computational and network overhead. In addition to this there is the extra computational overhead of needing to be simulate objects twice.

\subsection{Over network object collisions}
Objects in the overlapping region interact over the network. This could be done synchronously, which would be slow (could divide collision responses between servers and then exchange results). This solution would have to simulate objects twice and would require multiple round-trips of messages over the network per physics time-step, but the collision response for objects would be identical on both servers.

@@

\subsection{Remote objects as static}
Treat objects being simulated on another server as static. However, this would not lead to correct collision response, if compared to a single simulation. Momentum is conserved in collisions and no momentum is transferred to static objects, therefore the resulting momentum on the colliding object would not be the same as if the two objects were dynamic (not static) on a single simulation.
Half of all collisions would be missed, as collisions would be resolved for the object not being treated as static, but on the remote server, the collision never appears to happen, as the collision has already been resolved when receiving the updated state of the interacting object.
This could also lead to jitter, if two objects are in contact (i.e. colliding over multiple frames, such as a box stacked on top of another box), the server in which the collision is resolved on could be different every physics step, the outcome of which may be different and cause jitter.
% It is probably more complicated than this, as physics engines do a lot to deal with objects in contact, constantly moving a static object is probably going to interfere with this.

@@

>>>>

\subsection{Both servers simulate objects in an overlapping region}
Simulate objects overlapping the boundary and objects interacting with those on both servers, e.g. by using an overlapping region. Object may interact with objects not in the overlapping region, so the results would diverge or the overlapping region would have to dynamically change in order to keep all interacting objects within the overlapping region. Even if all objects interacting were in the overlapping region, results would still diverge due to non-determinism of physics engines. The divergence of results due to non-determinism could be corrected by periodically syncing the objects (ensuring the objects have the same state on both servers), however, this would appear as jitter as objects would be moved from one position to their corrected position instantaneously. In addition, this would require additional network overhead for the syncing of objects between servers and extra computational overhead of needing to simulate objects twice.

There would be a trade-off with this approach, either:
1) Frequent messages are sent with small corrections for objects, appearing as jitter. This would require lots of computational and network overhead. 
2) Infrequent messages with large corrections for objects, appearing as objects moving large distances instantaneously but would require less computational and network overhead.

For new objects entering the overlapping region, there will be a delay before the new object appears on both servers, network delays would affect this and could lead to the two simulations diverging significantly. For example, if there are two fast moving objects on a collision course with each other that are expected to collide in the overlapping region. Due to network delays, each server only becomes aware of the other object once the objects have already passed each other, as a result the collision is missed entirely and the result is incorrect compared to a single simulation.
%For example, a newly entered object from one server knocked over a stack of cubes in the overlapping region, if there was a long delay in communication, the receiving server might one physics timestep be unaware of any collision, the next timestep it would update to many timesteps after the collision

\subsection{Over network object collisions}
Objects in the overlapping region interact over the network. This would be done with the two physics in lock-step, i.e. neither progresses until all computation divided between the servers has been completed for that physics step. Servers could divide the computation of collision detection and/or response between servers and then exchange results. This solution would have to simulate objects twice and would require multiple round-trips of messages over the network per physics time-step, but the collision response for objects would be identical on both servers. This approach would be affected by network delays significantly, as not only are multiple round-trips of messages required between server each physics time-step, the simulation won't advance until all messages for that physics time-step have been completed, meaning the frequency of the simulation would be negatively affected.

@@

\subsection{Remote objects as static}
Treat objects being simulated on another server as static. However, this would not lead to correct collision response, if compared to a single simulation. Momentum is conserved in collisions and no momentum is transferred to static objects, therefore the resulting momentum on the colliding object would not be the same as if the two objects were dynamic (not static) on a single simulation.
Half of all collisions would be missed, as collisions would be resolved for the object not being treated as static, but on the remote server, the collision never appears to happen, as the collision has already been resolved when receiving the updated state of the interacting object.
This could also lead to jitter, if two objects are in contact (i.e. colliding over multiple frames, such as a box stacked on top of another box), the server in which the collision is resolved on could be different every physics step. An cube stacked on top of a static cube may have a different outcome to a cube with a static cube stacked on top of it.
% It is probably more complicated than this, as physics engines do a lot to deal with objects in contact, constantly moving a static object is probably going to interfere with this.

@@

This approach would be affected by network delays. For example, using the stacked cubes example. Say the two cubes are free-falling. If the bottom cube was being simulated on a different server, the position of the bottom cube would only be updated whenever a message was received from the remote server to do so. If there was a long delay between messages from the remote server, for example, from a spike in latency or a sudden big loss in packets, the cube would not be updated and appear to have stopped falling. As the bottom cube has stopped on the receiving server, the top cube remains stationary, as it is in contact with the bottom cube. On the remote server, if messages are being received, the cube would be stationary and appear to be floating, as from its server's perspective, it is in contact with the bottom cube. As a result, both servers have incorrect states compared to a single simulation.
